Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-02-02 Manuscript/manuscript.Rmd
updated todo and manuscript

Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1). The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments for the GM12878, K562, ... cell lines. Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.

>>>>

Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1). The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments for the GM12878 and K562 cell lines. Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
